---
title: "Shiny_HW"
date: '2024-11-15'
author: 'Ruihang Han'
output: html_document
runtime: shiny
---

```{r}
library(shiny)
```

Hadley_1

```{r}
ui <- fluidPage(
  selectInput("dataset", label = "Dataset", choices = ls("package:datasets")),
  verbatimTextOutput("summary"),
  tableOutput("table")
)


server <- function(input, output, session) {
  output$summary <- renderPrint({
    dataset <- get(input$dataset, "package:datasets")
    summary(dataset)
  })
  
  output$table <- renderTable({
    dataset <- get(input$dataset, "package:datasets")
    dataset
  })
}

shinyApp(ui, server)
```

Hadley_2
```{r}
library(shiny)

ui <- fluidPage(
  titlePanel("Dataset Explorer"),
  sidebarLayout(
    sidebarPanel(
      selectInput("selected_dataset", label = "Select a Dataset", 
                  choices = ls("package:datasets"), 
                  selected = "mtcars")
    ),
    mainPanel(
      h4("Summary of the Dataset"),
      verbatimTextOutput("dataset_summary"),
      h4("Preview of the Dataset"),
      tableOutput("dataset_table")
    )
  )
)

server <- function(input, output, session) {
  # Reactive function to retrieve the chosen dataset
  chosen_data <- reactive({
    get(input$selected_dataset, "package:datasets")
  })

  output$dataset_summary <- renderPrint({
    # Call reactive function
    summary(chosen_data())
  })

  output$dataset_table <- renderTable({
    # Display first 15 rows to keep the output manageable
    head(chosen_data(), 15)
  })
}

shinyApp(ui, server)
```



2.3.5
# 1. Pair render functions with output functions
library(shiny)

# App with verbatimTextOutput for renderPrint(summary(mtcars))
```{r}
ui <- fluidPage(verbatimTextOutput("summary_output"))
server <- function(input, output, session) { output$summary_output <- renderPrint({ summary(mtcars) }) }
shinyApp(ui, server)
```

# App with textOutput for renderText("Good morning!")
```{r}
ui <- fluidPage(textOutput("text_output"))
server <- function(input, output, session) { output$text_output <- renderText({ "Good morning!" }) }
shinyApp(ui, server)
```

# App with verbatimTextOutput for renderPrint(t.test(1:5, 2:6))
```{r}
ui <- fluidPage(verbatimTextOutput("ttest_output"))
server <- function(input, output, session) { output$ttest_output <- renderPrint({ t.test(1:5, 2:6) }) }
shinyApp(ui, server)
```

# App with verbatimTextOutput for renderText(str(lm(mpg ~ wt, data = mtcars)))
```{r}
ui <- fluidPage(verbatimTextOutput("lm_output"))
server <- function(input, output, session) { output$lm_output <- renderPrint({ str(lm(mpg ~ wt, data = mtcars)) }) }
shinyApp(ui, server)
```

# 2. Customized Shiny app with scatterplot and alt text
```{r}
ui <- fluidPage(plotOutput("scatterplot"))
server <- function(input, output, session) { output$scatterplot <- renderPlot({ plot(runif(5), runif(5), main = "Scatterplot of Random Numbers") }) }
shinyApp(ui, server)
```
# 3. renderDataTable() with options to suppress controls
```{r}
library(DT)
ui <- fluidPage(DTOutput("table"))
server <- function(input, output, session) { output$table <- renderDataTable(mtcars, options = list(pageLength = 5, searching = FALSE, ordering = FALSE, info = FALSE, lengthChange = FALSE, paging = FALSE)) }
shinyApp(ui, server)
```

# 4. reactable instead of renderDataTable
```{r}
library(reactable)
ui <- fluidPage(reactableOutput("table"))
server <- function(input, output, session) { output$table <- renderReactable({ reactable(mtcars, pagination = FALSE) }) }
shinyApp(ui, server)
```

3.3.6

1.
```{r}
ui <- fluidPage(
  textInput("name", "What's your name?"),
  textOutput("greeting")
)
```

```{r}
server1 <- function(input, output, session) {
  output$greeting <- renderText({
    paste0("Hello ", input$name)
  })
}
server2 <- function(input, output, session) {
  output$greeting <- renderText({
    paste0("Hello ", input$name)
  })
}
server3 <- function(input, output, session) {
  output$greeting <- renderText({
    paste0("Hello ", input$name)
  })
}
shinyApp(ui, server)

```
2.
 reactive graph1

input$a  input$b
   |        |
   V        V
      reactive(c) (c <- input$a + input$b)
                 |
                 V
       input$d  reactive(e) (e <- c() + input$d)
            |          |
            V          V
                 output$f (renderText(e()))



  reactive graph2

input$x1  input$x2  input$x3
    |        |        |
    V        V        V
       reactive(x) (x <- input$x1 + input$x2 + input$x3)

input$y1  input$y2
    |        |
    V        V
       reactive(y) (y <- input$y1 + input$y2)
                 |
                 V
         output$z (renderText(x() / y()))


  reactive graph3
  input$a    input$b      input$c       input$d
   |         |            |             |
   V         V            V             V
reactive(a) reactive(b) reactive(c)  reactive(d)
(a <- input$a * 10)  (b <- a() + input$b)  (c <- b() / input$c)  (d <- c() ^ input$d)

3.
```{r}
# Define a reactive variable for the selected column
selected_var <- reactive(df[[input$var]])

# Define a reactive expression for the range of the selected variable
selected_var_range <- reactive({
  range(selected_var(), na.rm = TRUE)
})


```
This code will fail due to a naming conflict.  
In R, `range` is a built-in function, so using it as the name of a reactive expression can cause unexpected errors or behavior.  
To avoid overriding the base function, it's recommended to use a different name for the reactive expression.

4.8
1.

                    ┌───────────────┐
                    │ input$code    │
                    └──────┬────────┘
                           │
                 ┌─────────▼───────────┐
                 │ selected()          │
                 │ (filters injuries   │
                 │  based on prod_code)│
                 └───┬──────────┬──────┘
                     │          │
        ┌────────────▼───┐ ┌────▼────────────┐
        │ output$diag    │ │ output$body_part│
        │ (table count   │ │ (table count    │
        │  by diag)      │ │  by body_part)  │
        └────────────────┘ └─────────────────┘
                      │
                      │
                  ┌───▼───────────────┐
                  │ output$location   │
                  │ (table count      │
                  │  by location)     │
                  └───▲───────────────┘
                      │
              ┌───────┴───────────────┐
              │ summary()             │
              │ (count by age, sex,   │
              │  then joined with     │
              │  population)          │
              └─────────┬─────────────┘
                        │
             ┌──────────▼────────────┐
             │ output$age_sex        │
             │ (line plot by age,    │
             │  n per age-sex group) │
             └────────────────────────┘




                    ┌───────────────┐
                    │ input$code    │
                    └──────┬────────┘
                           │
                 ┌─────────▼───────────┐
                 │ selected()          │
                 │ (filters injuries   │
                 │  based on prod_code)│
                 └───┬──────────┬──────┘
                     │          │
        ┌────────────▼───┐ ┌────▼────────────┐
        │ output$diag    │ │ output$body_part│
        │ (table count   │ │ (table count    │
        │  by diag)      │ │  by body_part)  │
        └────────────────┘ └─────────────────┘
                      │
                      │
                  ┌───▼───────────────┐
                  │ output$location   │
                  │ (table count      │
                  │  by location)     │
                  └───▲───────────────┘
                      │
              ┌───────┴───────────────┐
              │ summary()             │
              │ (count by age, sex,   │
              │  then joined with     │
              │  population)          │
              └─────────┬─────────────┘
                        │
          ┌─────────────▼────────────────────────────┐
          │ input$y                                 │
          │ (user choice: rate vs count)            │
          └─────────────┬───────────────────────────┘
                        │
             ┌──────────▼────────────┐
             │ output$age_sex        │
             │ (conditional plot by  │
             │  age: rate or count   │
             │  based on input$y)    │
             └────────────────────────┘




                    ┌───────────────┐
                    │ input$code    │
                    └──────┬────────┘
                           │
                 ┌─────────▼───────────┐
                 │ selected()          │
                 │ (filters injuries   │
                 │  based on prod_code)│
                 └───┬──────────┬──────┘
                     │          │
        ┌────────────▼───┐ ┌────▼────────────┐
        │ output$diag    │ │ output$body_part│
        │ (table count   │ │ (table count    │
        │  by diag)      │ │  by body_part)  │
        └────────────────┘ └─────────────────┘
                      │
                      │
                  ┌───▼───────────────┐
                  │ output$location   │
                  │ (table count      │
                  │  by location)     │
                  └───▲───────────────┘
                      │
              ┌───────┴───────────────┐
              │ summary()             │
              │ (count by age, sex,   │
              │  then joined with     │
              │  population)          │
              └─────────┬─────────────┘
                        │
             ┌──────────▼────────────┐
             │ output$age_sex        │
             │ (conditional plot by  │
             │  age: rate or count)  │
             └──────────┬────────────┘
                        │
             ┌──────────▼────────────┐
             │ input$story           │
             └──────────┬────────────┘
                        │
            ┌───────────▼─────────────┐
            │ narrative_sample()      │
            │ (gets new narrative     │
            │  on button click)       │
            └───────────┬─────────────┘
                        │
              ┌─────────▼──────────────┐
              │ output$narrative       │
              │ (displays current      │
              │  narrative text)       │
              └────────────────────────┘






2.
If you flip fct_infreq() and fct_lump(), the code will lump all values first, then order by frequency.
This would lead to a less accurate table where less common factors may end up lumped with more common ones, affecting the interpretability and accuracy of the summarized table.

3.

#column(4, sliderInput("num_rows", "Number of rows:", min = 1, max = 10, value = 5))

#output$diag <- renderTable(count_top(selected(), diag, n = input$num_rows), width = "100%")
#output$body_part <- renderTable(count_top(selected(), body_part, n = input$num_rows), width = "100%")
#output$location <- renderTable(count_top(selected(), location, n = input$num_rows), width = "100%")


4.
```{r}
fluidRow(
  column(1, actionButton("prev_story", "Previous")),
  column(1, actionButton("next_story", "Next")),
  column(10, textOutput("narrative"))
)

```


#narrative_index <- reactiveVal(1)

#observeEvent(input$next_story, {
#  current <- narrative_index()
#  narrative_index(min(current + 1, nrow(selected())))
#})

#observeEvent(input$prev_story, {
#  current <- narrative_index()
#  narrative_index(max(current - 1, 1))
#})

#output$narrative <- renderText({
#  selected() %>% pull(narrative) %>% .[narrative_index()]
#})



